% ---
% Sadeli's Resume
% July 2023
% ---

\documentclass{article}

% ---
% Fancy resume formatting
% ---
\usepackage{titling}		            % Title formatting
\usepackage{titlesec}		            % Section formatting
\usepackage{fontawesome}	          % Icons
\usepackage{enumitem}		            % Remove \item spacing
\usepackage{hyperref}		            % Clickable hyperlinks
\usepackage{bookmark}               % Get rid of bookmark warnings
\usepackage[margin=0.5in]{geometry}	% Don't make the page so small

\pagenumbering{gobble}  % Remove page numbering
\setlist[itemize]{noitemsep, topsep=0pt}

% Title formatting
\renewcommand{\maketitle}{
  \begin{center}
  {\Large \theauthor}
  {\vspace{0.1in}}

  % Add contact info here
  \faEnvelopeO \ \href{mailto:redacted@redacted.com}{redacted@redacted.com} \hspace{.2in} \faMobile \ (123) 456-7890 \hspace{.2in} \faGithubSquare \ \url{https://github.com/sadeli413} \hspace{.2in} \faLinkedinSquare \ \href{https://www.linkedin.com}{redacted-linkedin} \hspace{.2in}
  \end{center} 
}

% Section Formatting
\titleformat{\section}
{\large \uppercase}{}{0em}{}[\titlerule] % horizontal line

% Subsection with a date parameter
\newcommand{\resumesubsection}[2]{
	\noindent \textbf{#1} \hfill #2
}

% Subsection formatting
\titleformat{\subsection}
{\bfseries}{}{0em}{} % Bold

\titlespacing{\subsection}
{0em}{0em}{0em} % No space

% Subsubsection formatting
\titleformat{\subsubsection}
{}{}{0em}{}

\titlespacing{\subsubsection}
{0em}{0em}{0em}

% item formatting
\titlespacing{\item}
{0em}{0em}{0em}

% ---
% Resume starts here
% ---
\begin{document}

% Title
\title{Resume}
\author{Sadeli 413}
\maketitle

% About Me
\section{About Me}

\subsection{Technical Skills}
\begin{itemize}
	\item Docker, Ghidra, Ida Pro, Wireshark, GDB, LLDB, Pwntools, Kali Linux, Sliver, Nmap, Ffuf, Vmware, Burp Suite
\end{itemize}
\subsection{Programming Languages}
\begin{itemize}
  \item Rust, Python, Go, Bash, C, x86 Assembly, ARM Assembly
\end{itemize}

% Work Experience
\section{Work Experience}

\resumesubsection{Battelle Memorial Institute}{May 2023 - Present}
\subsubsection{Reverse Engineer and Vulnerability Researcher}
\begin{itemize}
  \item Utilized static analysis and dynamic analysis tools to reverse engineer embedded devices and communication protocols.
  \item Engineered fuzzing harnesses to discover weaknesses and developed exploitation scripts to target vulnerable devices.
\end{itemize}

\resumesubsection{Lawrence Livermore National Laboratory}{May 2022 - May 2023}
\subsubsection{Cyber Security Intern | Cyber Testing for Resilient Industrial Control Systems}
\begin{itemize}
  \item Scripted Ghidra in Python to detect supply-chain components in firmware for industrial control systems.
  \item Utilized machine learning techniques such as random forests and clustering to compute similarities between binaries.
\end{itemize}

\resumesubsection{Honeywell Global Security}{May 2021 - August 2021}
\subsubsection{Cyber Security Intern | Vulnerability Management Team}
\begin{itemize}
  \item Performed vulnerability audits for over 300,000 assets including over 900 web applications and consulted internal development teams to remediate vulnerabilities.
  \item Automated the generation of client-readable reports from Rapid7 InsightVM and Qualys WAS vulnerability scan data.
\end{itemize}

\resumesubsection{ASU Research Enterprise}{November 2020 - May 2021}
\subsubsection{Student Developer | Research Consultant}
\begin{itemize}
  \item Designed and deployed an IoT hacking and cybersecurity course and trained over 20 US veterans and Navy ROTC students.
  \item Demonstrated drone hacking, radio replay attacks, WIFI attacks, hardware hacking, and firmware exploitation.
\end{itemize}

% Education
\section{Education}

\resumesubsection{Arizona State University}{August 2019 - May 2023}
\begin{itemize}
  \item B.S. Computer Science | GPA: 3.96
\end{itemize}

\subsection{Certifications}
\begin{itemize}
    \item CompTIA A+ (2020)
    \item CompTIA Network+ (2021)
\end{itemize}

% Other Activities
\section{Activities}

\resumesubsection{Hack The Box}{August 2019 - Present}
\subsubsection{Rank: Hacker}
\begin{itemize}
  \item Played CTFs to learn web app reconnaissance and exploitation, privilege escalation techniques, and offensive tooling.
  \item \faCube \ \url{https://www.hackthebox.eu/profile/171856}{}
\end{itemize}

\resumesubsection{Pwn College}{August 2022 - Present}
\subsubsection{Rank: Yellow Belt}
\begin{itemize}
  \item Played CTFs to learn binary exploitation techniques such as ROP, JIT spraying, and sandbox escapes.
  \item \url{https://pwn.college/hacker/233}
\end{itemize}

\resumesubsection{Western Regional Collegiate Cyber Defense Competition}{January 2021 - April 2023}
\subsubsection{Blue Team Member}
\begin{itemize}
	\item Hardened Linux machines, patched misconfigured services, and participated in incident response to isolate cyber threats.
  \item Represented ASU and placed 3rd in the 2022 and 2023 Western Regional competitions.
\end{itemize}

\resumesubsection{DevilSec}{August 2019 - May 2023}
\subsubsection{Officer | Secretary}
\begin{itemize} 
	\item Gave talks on red team methodologies, penetration testing tools, and network security.
  \item Developed and deployed Hack The Box-style CTF challenges for club members in a Docker environment on AWS.
\end{itemize}

\end{document}
